Classless Java

### 2015-09-21 paper/sections/Overview.tex
revised overview

Interface \texttt{Point3D} extends \texttt{Point/Point2D} with a new abstract
method \texttt{int z()} (treated as a member field). Interface \texttt{Horse}
shows the usage and advantage of \emph{with} methods by method
\texttt{run()}. Note that the return type of various methods get refined
automatically by our annotation processor. Besides \emph{with}, other methods
(including \emph{clone}, \emph{of}) also do type-refinements automatically.

The \emph{``multiple inheritance''} case appears at interface
\texttt{Pegasus}. Pegasuses can not only run but also fly! Interface
\texttt{Pegasus} obtains \texttt{fly} and \texttt{run} functionality through
interface \texttt{Horse} and \texttt{Bird}. Using \mixin annotation, actually
these is no code at all programmars have to write, which otherwise is hard
to do in Java-like languages that do not support multiple inheritance.

>>>>

Interface \texttt{Point3D} extends \texttt{Point/Point2D} with a new abstract
method \texttt{int z()} (treated as a getter for member field
\texttt{z}). Interface \texttt{Horse} shows the usage and advantage of
\emph{with} methods by method \texttt{run()}: method \texttt{withX} returns a
new point object with field \texttt{x} updated by the argument to
\texttt{withX}. Without these \texttt{with} methods, operations like
\texttt{run()} would be much harder to define. Note that the return type of
various methods get refined automatically by our annotation processor. Besides
\emph{with}, other methods (including \emph{clone}, \emph{of}) also do
type-refinements automatically.

The \emph{``multiple inheritance''} case appears at interface
\texttt{Pegasus}. Pegasuses can not only \emph{run} but also \emph{fly}!
Interface \texttt{Pegasus} obtains \texttt{fly} and \texttt{run} functionality
through interface \texttt{Horse} and \texttt{Bird}. Using \mixin annotation,
actually these is no code at all programmers have to write. The idea of using
default methods inside interfaces was proposed in ~\cite{}. It enables us to do
multiple inheritance, which otherwise is hard to do in Java-like languages that
do not support multiple inheritance, easily.
